Compiling refinement types to dependent types

### 2020-07-20 tex/paper.tex
Better define \tranctx

\paragraph{Contexts.}
We start with defining $\tranctx$,
which merely translates the types of the bindings in the context from the surface language into the core language:
\begin{equation}
\begin{aligned}
  & \tranctx(\emptyset)                                       && \triangleq \emptyset                                               \\
  & \tranctx(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \tranctx(\nonterm G), \gterm x : \tranty(\nonterm{ts})  \\
\end{aligned}
\end{equation}

>>>>

\paragraph{Contexts.}
We start with defining $\tranctx$,
which is the simplest translation of the three.
It merely maps the types of the bindings in a (well-formed) context
from the surface language into the core language.

\begin{equation}
\begin{aligned}
  & \tranctx(\emptyset)
      && \triangleq
    \emptyset                                               \\
  & \tranctx(\nonterm G, \gterm x : \nonterm{ts})
      && \triangleq
    \tranctx(\nonterm G), \gterm x : \tranty(\nonterm {G} \vdash \nonterm{ts})  \\
\end{aligned}
\end{equation}
